### 2023-04-06 papers.tex
resolving updates author draft revisions

\addtrack{E}{Publishing, Meet Perishing}
\addpaper
	{TeX-to-TikZ}
	{Alex Friedman, Charlotte Clark, Natalie McClain, Shaw-leon Chen, Connie Chau, Jake Backer, N'yoma Diamond, and Rose Bohrer}
	{}
	{SIGBOVIK_2023_paper_13.pdf}
	{0cm}
	{}
\addpaper
	{Cerberus: Why Papers Named Cerberus Always Get Accepted}
	{Ben Weintraub}
	{}
	{SIGBOVIK_2023_paper_28.pdf}
	{0cm}
	{}
\addpaper
	{Large Language Models are Few-Shot Publication Scoopers}
	{Samuel Albanie, Liliane Momeni, and Joao F. Henriques}
	{}
	{SIGBOVIK_2023_paper_42.pdf}
	{0cm}
	{}
\addpaper
	{Author-Unification: Name-, Institution-, and Career-Sharing Co-authors}
	{Vanessa Wirth, Vanessa Wirth}
	{}
	{SIGBOVIK_2023_paper_45.pdf}
	{0cm}
	{}

@@

\addtrack{I}{Line of Inquiry, Meet Your Logical Conclusion}
\addpaper
	{Unlimited null: achieving memory safety by extending memory protection}
	{hikari\_no\_yume}
	{}
	{SIGBOVIK_2023_paper_14.pdf}
	{0cm}
	{}
\addpaper
	{miles2km: The worst ways to convert from miles to km}
	{Lucien Rae}
	{}
	{SIGBOVIK_2023_paper_30.pdf}
	{0cm}
	{}
\addpaper
	{Alan Hsu}
	{Alex Xie and Alan Hsu}
	{}
	{SIGBOVIK_2023_paper_35.pdf}
	{0cm}
	{}
\addpaper
	{ACHOO: Actually Higher Order Optimization}
	{Clayton W Thorrez}
	{}
	{SIGBOVIK_2023_paper_57.pdf}
	{0cm}
	{}
\addpaper
	{The Phonetic Portmantout}
	{Kyle A. Williams}
	{}
	{SIGBOVIK_2023_paper_58.pdf}
	{0cm}
	{}
\addpaper
	{An Introduction to Compliers}
	{Anoushka Shrivastava}
	{}
	{SIGBOVIK_2023_paper_63.pdf}
	{0cm}
	{}

@@

\addtrack{L}{Hunger, Meet Pickle}
\addpaper
	{The Influence of Lunch Items on Cryptocurrency in the United States}
	{\protect {*David An [0x7e7]}}
	{}
	{SIGBOVIK_2023_paper_7.pdf}
	{0cm}
	{}
\addpaper
	{}
	{}
	{}
	{SIGBOVIK_2023_paper_41.pdf}
	{0cm}
	{}
\addpaper
	{Tactical Toast Cut Silhouette Recognition Guide}
	{Jim McCann}
	{}
	{SIGBOVIK_2023_paper_62.pdf}
	{0cm}
	{}
\addpaper
	{Saltgurken: A formal grammar for unambiguous grocery shopping}
	{*Eleftheria Chatziargyriou}
	{}
	{SIGBOVIK_2023_paper_34.pdf}
	{0cm}
	{}

>>>>

\addtrack{E}{Publishing, Meet Perishing}
\addpaper
	{TeX-to-TikZ}
	{Alex Friedman, Charlotte Clark, Natalie McClain, Shaw-leon Chen, Connie Chau, Jake Backer, N'yoma Diamond, and Rose Bohrer}
	{}
	{SIGBOVIK_2023_paper_13.pdf}
	{0cm}
	{}
\addpaper
	{Cerberus: Why Papers Named Cerberus Always Get Accepted}
	{Ben Weintraub}
	{}
	{SIGBOVIK_2023_paper_28.pdf}
	{0cm}
	{}
\addpaper
	{Large Language Models are Few-Shot Publication Scoopers}
	{Samuel Albanie, Liliane Momeni, and Joao F. Henriques}
	{}
	{SIGBOVIK_2023_paper_42.pdf}
	{0cm}
	{}
\addpaper
	{Author-Unification: Name-, Institution-, and Career-Sharing Co-authors}
	{Vanessa Wirth, Vanessa Wirth}
	{}
	{SIGBOVIK_2023_paper_45.pdf}
	{0cm}
	{}
\addpaper
	{The Time's Come: Proof-of-Concept Study Discussing Linguistic-Cognitive Influences Supporting the Deletion of the Letter ``A''}
	{Danielle R. Thomas, Cindy Tipper, Shivang Gupta, Joe Kopko, Hui Cheng, John Lawson, }
	{}
	{SIGBOVIK_2023_paper_16.pdf}
	{0cm}
	{}

@@

\addtrack{I}{Line of Inquiry, Meet Your Logical Conclusion}
\addpaper
	{Unlimited null: achieving memory safety by extending memory protection}
	{hikari\_no\_yume}
	{}
	{SIGBOVIK_2023_paper_14.pdf}
	{0cm}
	{}
\addpaper
	{miles2km: The worst ways to convert from miles to km}
	{Lucien Rae}
	{}
	{SIGBOVIK_2023_paper_30.pdf}
	{0cm}
	{}
\addpaper
	{Fun for the Whole Family: Fast and Furious Transforms}
	{Alex Xie, Alan Hsu, and Abhishek Vijayakumar}
	{}
	{SIGBOVIK_2023_paper_35.pdf}
	{0cm}
	{}
\addpaper
	{ACHOO: Actually Higher Order Optimization}
	{Clayton W Thorrez}
	{}
	{SIGBOVIK_2023_paper_57.pdf}
	{0cm}
	{}
\addpaper
	{The Phonetic Portmantout}
	{Kyle A. Williams}
	{}
	{SIGBOVIK_2023_paper_58.pdf}
	{0cm}
	{}
\addpaper
	{An Introduction to Compliers}
	{Anoushka Shrivastava}
	{}
	{SIGBOVIK_2023_paper_63.pdf}
	{0cm}
	{}

@@

\addtrack{L}{Hunger, Meet Pickle}
\addpaper
	{The Influence of Lunch Items on Cryptocurrency in the United States}
	{\protect {*David An [0x7e7]}}
	{}
	{SIGBOVIK_2023_paper_7.pdf}
	{0cm}
	{}
\addpaper
	{}
	{}
	{}
	{SIGBOVIK_2023_paper_41.pdf}
	{0cm}
	{}
\addpaper
	{Tactical Toast Cut Silhouette Recognition Guide}
	{Jim McCann}
	{}
	{SIGBOVIK_2023_paper_62.pdf}
	{0cm}
	{}
\addpaper
	{Salzgurken: A formal grammar for unambiguous grocery shopping}
	{*Eleftheria Chatziargyriou}
	{}
	{SIGBOVIK_2023_paper_34.pdf}
	{0cm}
	{}
